\documentclass[margin,line]{res}
\usepackage{hyperref}
\usepackage{url}
\usepackage{breqn}
\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
\topmargin=0in
\topskip=0in
 
\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}


    
\begin{document}

\name{\LARGE DR. SHAHID ALI} \hfill {\em \today}

\begin{resume}
\section{CONTACT INFORMATION}
\vspace{.05in}
\begin{tabular}{@{}p{3.5in}p{3in}}
Associate Professor (Tenured)             & {Phone:}  (+92) 091-1234567 \\
Department of Physics 
 & {Cell:}  (+92) 0300-123456 \\
University of Peshawar             & {E-mail:}  \url{sayphysics@uop.edu.pk}\\
25120 Peshawar, Pakistan.  & 
{Website:}\url{http://www.uop.edu.pk}
\end{tabular}

\section{PERSONAL INFORMATION}
\vspace{.05in}
\begin{tabular}{@{}p{2.7in}p{3in}}

Father Name:	Father Name             & {Place of Birth:}		City\\
Date of Birth:		01-01-2000        & {Domicile:}		City, Province\\
\end{tabular}

\section{RESEARCH \\FIELDS}
-- Fabrication of metal ions doped glasses by field-assisted solid-state ion diffusion technique\\
-- Physics and chemistry of the diffusion process and precipitation of the nanoparticles in glass\\

\section{EDUCATION}
{\bf University or Institute}, City, Country \hfill August 2011 -- March 2012\\
Degree\\ 
Research Field:	X-Ray Absorption Fine Structure (XAFS) Spectroscopy\\
Supervisor:		Dr. Khan\\

\section{PROFESSIONAL\\EXPERIENCE}
{\bf University of Peshawar}, Peshawar, Pakistan \hfill March 2016 -- Present\\
Associate Professor \hfill(3 Years and 7 Months)

{\bf University of Peshawar}, Peshawar, Pakistan \hfill September 2012 -- 
March 2016\\
Assistant Professor \hfill(3 Years and 6 Months)

\section{RESEARCH\\FUNDING}
\begin{list2}
\item {\bf PKR 20m, HEC--NRPU project 2019--2021} Novel solar cell 
coverglass, HEC, Pakistan.
\item {\bf PKR 5.0m EU Erasmus+ Mobility 2017--2021} Mobility project 
\end{list2}

\section{AWARDS AND FELLOWSHIPS}
\vspace{.05in}
\begin{tabular}{@{}p{1.3in}p{4.4in}}

September 2011 & {Postdoctoral fellowship}\\
September 2005 & {PhD fulltime fellowship} \\ 
\end{tabular}
\section{PUBLICATIONS} 
{\bf IF Journals = 37,	Total IF = 125,  Avg. IF=3.4		Citations = 
218,     
h-index = 8}\\{ORCID iD:}\url{https://orcid.org/0000-0002-0121-3215}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{enumerate}
\item Shahid Ali \textit{et al.}, Title, \textit{International Journal of 
Hydrogen Energy}, Vol. X, pp. X--X, \textbf{2020}.
\item Shahid Ali \textit{et al.}, Effect of B-site dopants on the electrical 
properties \textit{Journal of Materials Science}, Vol. X, pp. X--X, 
\textbf{2020}.
\end{enumerate}

\section{CONFERENCE PROCEEDINGS}
\begin{enumerate}
\item Shahid Ali \textit{et al.}, Effect of B-site dopants on the electrical 
properties, \textit{International Journal of Hydrogen 
	Energy}, Vol. X, pp. X--X, \textbf{2020}.
\item Shahid Ali \textit{et al.}, Effect of B-site dopants on the electrical 
properties \textit{Journal of Materials Science}, Vol. X, pp. X--X, 
\textbf{2020}.
\end{enumerate}

\section{REFERENCES}
1. {\bf Dr. Khan}\\ 
Details of the referee email: \url {sayphysics@uop.edu.pk}
\\2. {\bf Dr. Ali}\\ 
Details of the referee email: \url {sayphysics@uop.edu.pk}\\

\end{resume}

\end{document}




